Equalizer\\Programming and User Guide

### 2013-03-12 Developer/ProgrammingGuide/paper.tex
Merge cleanups

Equalizer uses the hwsd library for discovering local and remote GPUs and
network interfaces. Based on this information, a typical configuration is
dynamically compiled during the initialization of the application. The
auto-configuration uses the same format as the static configuration files. It
can be used to create template configurations by running a test application or
the eqServer binary and using the generated configuration, saved as
\textless session\textgreater.auto.eqc.

Please note that both hwsd and the hwsd ZeroConf module are optional and
requires hwsd and a ZeroConf implementation when Equalizer is compiled.

hwsd contains three components: a core library, local and remote discovery
modules as well as a ZeroConf daemon. The daemon uses the appropriate module to
query local GPUs and network interfaces and announces them using ZeroConf on the
local network.

@@

\begin{itemize}
\item The default value is \textsf{local} which uses all local GPUs and network
  interfaces queried using the cgl, glx, or wgl GPU module and the sys network
  module.
\item \textsf{--eq-config sessionname} uses the dns\_sd ZeroConf module of
  hwsd to query all GPUs and network interfaces in the subnet for the given
  session. The default session of the hwsd daemon is \textsf{default}. The
  found network interfaces are used to connect the nodes.
\item \textsf{--eq-config filename.eqc} loads a static configuration from the
  given ASCII file. The following sections describe how to write configuration
  files.
\end{itemize}

@@

The objects on slave ObjectMap instances are mapped explicitly, either by
providing an already constructed instance or using an implicit object creation
using \textsf{co::ObjectFactory}. The factory needs to be supplied upon
construction of \textsf{co::ObjectMap} and the implementation for creating the
desired object types. Implicitly created objects are owned by the object which
affects the lifetime of those objects considering unmapping operations caused
by deregister(), explicit unmapping or destruction of the slave instance
ObjectMap.

In Sequel, the \textsf{co::ObjectMap} is used to distribute and synchronize the
InitData and FrameData objects. Sequel adds the object IDs for both objects in
addition to the default ObjectMap for automatic mapping during first access.
The main advantage comes from the one point commit and synchronization which
automatically updates changed objects to their correct version.

>>>>

Equalizer uses the hwsd library for discovering local and remote GPUs as well as
network interfaces. Based on this information, a typical configuration is
dynamically compiled during the initialization of the application. The
auto-configuration uses the same format as the static configuration files. It
can be used to create template configurations by running a test application or
the eqServer binary and using the generated configuration, saved as \textless
session\textgreater.auto.eqc.

Please note that both hwsd and the hwsd ZeroConf module are optional and
require hwsd and a ZeroConf implementation when Equalizer is compiled.

hwsd contains three components: a core library, local and remote discovery
modules as well as a ZeroConf daemon. The daemon uses the appropriate module to
query local GPUs and network interfaces to announce them using ZeroConf on the
local network.

@@

\begin{itemize}
\item The default value is \textsf{local} which uses all local GPUs and network
  interfaces queried using the cgl, glx, or wgl GPU modules and the sys network
  module.
\item \textsf{--eq-config sessionname} uses the dns\_sd ZeroConf module of
  hwsd to query all GPUs and network interfaces in the subnet for the given
  session. The default session of the hwsd daemon is \textsf{default}. The
  found network interfaces are used to connect the nodes.
\item \textsf{--eq-config filename.eqc} loads a static configuration from the
  given ASCII file. The following sections describe how to write configuration
  files.
\end{itemize}

@@

The objects on slave ObjectMap instances are mapped explicitly, either by
providing an already constructed instance or using implicit object creation
through the \textsf{co::ObjectFactory}. The factory needs to be supplied upon
construction of the \textsf{co::ObjectMap} and implement creation of the desired
object types. Implicitly created objects are owned by the object map which
limits their lifetime. They are released upon unmapping caused by deregister(),
explicit unmapping or destruction of the slave instance ObjectMap.

In Sequel, the \textsf{co::ObjectMap} is used to distribute and synchronize all
objects to the rendering frames. The InitData and FrameData objects are
implicitely known and managed by Sequel, and other objects might be used in
addition. The commit and synchronization of the object map, and consequently all
its objects, is automatically performed in the correct places, most importantly
the commit at the beginning of the frame, and the sync when accessing an object
from the renderer.
